Reading Notes

### 2020-08-25 2pd.tex
fix all chktex errors

%%<why do opvs matter>
\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref \cite{Dou2013}. Parts (b)-(d) adapted from ref \cite{Miller2018c}.}
    \label{opv}
\end{wrapfigure}

@@

\begin{figure}[h!]
    \includegraphics[width=\linewidth]{images/NREL2020.pdf}
    \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present. The current state-of-the-art OPV research cell achieves 17.4\% efficiency. Data taken from \cite{NREL2020}.}
    \label{nrel}
\end{figure}

\cite{Lin2019} 17.4 \% efficiency mixing polymer fullerene device with transition metal disulfide.
\cite{Cui2019} champion solar cell chlorinated NFA 16.5\% efiiciency
%% new figure
%% TODO
%% opvs are vast
%% crystalline silicon levels off -- shottkey quessar (sp?) limit 34% efficient not much room for growth (blue)
%% what you can buy vs champion devices
%% opvs show room to grow
%% paying for themselves
%%underdog
In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see \autoref{opv} c).
The performance of an OPV device is intimately linked with the structure of the active layer:
With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.

% TODO
%% include fig of ITIC PTB7? p3ht, fullerene recent uptick with NFAs
%% look up the 17% solar cell--whats in it?
%% freedom in choosing our ingredients - can we get better than trial and error
\cite{Cui2019}
chlorinated ladder backbone acceptor 16\% PCE 
%% https://www.printedelectronicsworld.com/articles/15405/raynergy-new-world-record-on-certified-pce-13-28-single-junction-opv
signle junction with NFA

@@

For this research we propose to develop a flexible method for specifying coarse grain models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
We also propose to develop a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport calculations.
This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient but also the result may even be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
The number of OPV compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
A poly-3-hexylthiophene (P3HT):NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.%%<there aren't a lot of cg models that already exist for these new compounds>
It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/ITIC.pdf}
    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
    \label{itic}
\end{wrapfigure}

@@

%%<why morphology matters>
The morphology of the device can be affected by the processing conditions: temperature, solvents, and concentrations/ratios of the active compounds\cite{Ma2005,Hoppe2004a,Li2007}.
The interfacial area of the acceptor:donor regions\cite{Mazzio2015}, the regioregularity of the polymer\cite{Kim2006}, and electronic properties of the compounds\cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device. 
These changes in structure can strongly affect the device performance.
Molecular simulation allows us to "see" these atomic interactions and gain a deeper view into the driving forces behind the self assembly of these OPV morphologies and to understand what conditions create the best devices.
%%<segue into simulation>

\subsection*{Molecular Dynamics}
%EJ: Here or above: Why MD the right tool?
Molecular dynamics (MD) is a simulation tool which uses classical physics and statistical thermodynamics to sample the equilibrium states of a thermodynamic ensemble.
The MD algorithm integrates Newton's equations of motion to update the particle positions.
This process can be iterated until the system reaches equilibrium.
MD is the right tool for looking at the bulk structure of an OPV because we can simultaneously probe the thermodynamics which govern OPV self assembly and the kinetics that follow the device processing.
Other tools, like Monte Carlo (MC), may allow us to sample equilibrium states of an ensemble, but we would lose information about the dynamics.
MC is also inefficient for polymers because perturbing a long chain of particles requires a "cluster move", which is not parallelizable.

@@

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}
    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from \cite{punma}.}
    \label{bad}
\end{wrapfigure}

Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
$$ U_{LJ}(r_{i,j}) = 4\epsilon\big[\big(\frac{\sigma}{r_{i,j}}\big)^{12}-\big(\frac{\sigma}{r_{i,j}}\big)^{6}\big]$$
Where $i$ and $j$ are the particles separated by distance $r_{i,j}$.
The equilibrium distance between particles is controlled by $\sigma$ and the depth of the potential well is controlled by $\epsilon$ (see \autoref{lj}).
A distance cutoff, $r_{cut}$, is often used to reduce the number of pairwise interactions and improve performance.

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/lj.pdf}
    \caption{The Lennard-Jones potential with relevant distances labelled}
    \label{lj}
\end{wrapfigure}

Particles connected by bonds are also modelled by classical forces, for example the bond potential may be treated as a harmonic oscillator:
$$V_{bond}(r) = \frac{1}{2}k(r-r_{0})^{2}$$
Where $r$ is the bond length, $r_{0}$ is the equilibrium bond length, and $k$ is the spring constant for the bond.
The angle potential is also treated as a harmonic oscillator:
$$V_{angle}(\theta)=\frac{1}{2}k(\theta-\theta_{0})^{2}$$
Where $\theta$ is the angle formed between three bonded particles, $\theta_{0}$ is the equilibrium angle, and $k$ is the spring contant for the angle.
The dihedral potential can be defined by the follow Fourier series:
$$V_{dihedral}(\phi)=\frac{1}{2}k_{1}(1-cos(\phi))+\frac{1}{2}k_{2}(1-cos(2\phi))+\frac{1}{2}k_{3}(1-cos(3\phi))\frac{1}{2}k_{4}(1-cos(4\phi))$$
Where $\phi$ is the angle between planes formed by particles in the dihedral (see \autoref{bad}) and $k_{n}$ are the force coeffients.

%% transition???
The first MD simulation modelled a system of 108 particles and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
Now GPUs are a 100 millions times faster.
%%<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
Due to its efficient scaling, MD is now commonly used for the modelling of protein folding \cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.
By abstracting away some of the atomic degrees of freedom, MD can be used to look at even larger systems. %%transition attempt

@@

Coarse graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
%%<how do cg models let us access long length/time??>
Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest, we don't need to consider atomic level properties when we are interested in the bulk morphology\cite{Muller-Plathe2002}.
The heart of coarse graining is the removal of degrees of freedom. 
This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
Due to their long length and time scales, coarse grain models are ideal for examining polymer properties\cite{Gartner2019a}.
It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
Even if the simulation was to complete, there would be too much information to process accurately. 
Coarse graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.

The resolution of coarse grain systems is broad:
Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one bead per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
%%<examples of cg models and the cool things they do>
General coarse grain models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
A coarse grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
%% transition?
Which model is right depends on the length and time scale on which the property of interest can be observed.

%%<multiscale sims>
For many systems, however, we are interested in properties which span length scales.
For instance, in a system like a OPV polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)\cite{Huang2010}; it is the wrong tool for the job.
If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily: a process called backmapping.
In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse grain structure.
The large length scale, polymer level properties can be equilibrated during the coarse grain simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores \textit{and} the connectivity of these chromophores over distances proportional to the exciton dissociation length.
%%<what stands in our way?>

@@

%%<segue from automated creation of forcefields to...>
%%<mapping operator has to be decided by hand> <is this section too big?>
Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and where the site is placed relative to the atom group.
Mapping operators are chosen based on the desired resolution of the coarse grain system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule, you must pick a mapping and then compare the resulting beads to existing beads; a process which is time consuming and error prone\cite{martini-tutorial}.
%%The MARTINI force field was first designed for lipids, further parameterization for proteins and nuclei acids has since been added, and it has been shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
Many other mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend? What groups have the most dominant interactions in this structure). %%<cite any model where rings are one bead><cite dna cg model>).
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a "super-atom" bead.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
Another uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably\cite{Li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
%%<how cg potentials have been attained> 
Deciding on a mapping operator is one part of creating a coarse grain model, the second step is to create an effective potential for the site.

@@

There are numerous methods for deriving coarse grain potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
%%<IBI>
IBI is where a coarse grain potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
Here is the algorithm for determining the non-bonded potentials:
First the coarse grain system is mapped onto an equilibrated atomistic one.
Then the radial distribution function (RDF) of the mapped systems is calculated over the equilibrated frames of the trajectory--This is the target distribution.
Given any particle, the RDF gives the probability of finding a neighboring particle at distance r.
Taking the Boltzmann Inverse of the RDF results in the potential of mean force (PMF). %%<add equation>
%% equation
Then a CG simulation can be run using the PMF as the non-bonded potential to achieve a new distribution.
Then the difference between the new and target distribution can be accounted for in the next iteration accoring to equation %%<add equation>.
This process is repeated until the difference between the result and the target are sufficiently similar.

The coarse grain potential derived from IBI is not transferrable to different thermodynamic statepoints.
This is because the RDF is a property of the ensemble average at a given statepoint, so the potential derived from this property is also limited.
For example, separate potentials are required to capture solid and fluid structures of a pure simple lipid \cite{Hadley2010a}.
There are many attempts to create transferrable CG potentials, for example:
The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}.
But optimization to the liquid-vapor equilibrium, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.
%%<so we probably want to create our own potentials>
%%<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/moorefig.pdf}
    \caption{Visualization of the state space coverage of different potentials: if the thermodynamic states are too similar (b), then the overlap region is large enough that there are many potentials which will fit the target. Choosing states which are different (a) will better define the potential. Image adapted from ref \cite{Moore2014}.}
    \label{moore}
\end{wrapfigure}

Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential\cite{Moore2014}.
The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid.
When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
If this overlap region is large, there are many potentials which will provide matching RDFs (see \autoref{moore}).
For some systems there may not be a potential that represents all states; this is not unique to coarse potentials, atomistic potentials also have this limitation.
%%<need some tie in back to why we would want to go from CG-->atomistic>

@@

As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the bead chemistries. %%cite grits
This package will need further testing as it is tested on different compounds, but the proof of concept exists.

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
    \caption{Hexane chemical structure (top) overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}
    \label{hexane}
\end{wrapfigure}

>>>>

%%<why do opvs matter>
\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}\label{opv}
    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref~\cite{Dou2013}. Parts (b -- d) adapted from ref~\cite{Miller2018c}.} % chktex 8
\end{wrapfigure}

@@

\begin{figure}[h!]
    \includegraphics[width=\linewidth]{images/NREL2020.pdf}\label{nrel}
    \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present. The current state-of-the-art OPV research cell achieves 17.4\% efficiency. Data taken from~\cite{NREL2020}.}
\end{figure}

17.4 \% efficiency mixing polymer fullerene device with transition metal disulfide\cite{Lin2019}.
champion solar cell chlorinated NFA 16.5\% efiiciency\cite{Cui2019}. 
%% new figure
%% TODO
%% opvs are vast
%% crystalline silicon levels off --- shottkey quessar (sp?) limit 34% efficient not much room for growth (blue)
%% what you can buy vs champion devices
%% opvs show room to grow
%% paying for themselves
%%underdog
In order to make the most efficient OPVs we need to find the blend of compounds and processing conditions that result in the best structure for those compounds.
The active layer of an OPV is mixture of electron-donor and acceptor compounds: the ideal morphology is a micro phase-separated interpenetrating network called a bulk heterojunction (BHJ) (see \autoref{opv} c).
The performance of an OPV device is intimately linked with the structure of the active layer:
With minor modifications, the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.

% TODO
%% include fig of ITIC PTB7? p3ht, fullerene recent uptick with NFAs
%% look up the 17% solar cell---whats in it?
%% freedom in choosing our ingredients - can we get better than trial and error
%% https://www.printedelectronicsworld.com/articles/15405/raynergy-new-world-record-on-certified-pce-13-28-single-junction-opv
signle junction with NFA

@@

For this research we propose to develop a flexible method for specifying coarse grain models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
We also propose to develop a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport calculations.
This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient but also the result may even be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
The number of OPV compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
A poly-3-hexylthiophene (P3HT):NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.%%<there aren't a lot of cg models that already exist for these new compounds>
It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/ITIC.pdf}\label{itic}
    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
\end{wrapfigure}

@@

%%<why morphology matters>
The morphology of the device can be affected by the processing conditions: temperature, solvents, and concentrations/ratios of the active compounds\cite{Ma2005,Hoppe2004a,Li2007}.
The interfacial area of the acceptor:donor regions\cite{Mazzio2015}, the regioregularity of the polymer\cite{Kim2006}, and electronic properties of the compounds\cite{Scharber2006a} all play an important role in the power conversion efficiency (PCE) of the device. 
These changes in structure can strongly affect the device performance.
Molecular simulation allows us to ``see'' these atomic interactions and gain a deeper view into the driving forces behind the self assembly of these OPV morphologies and to understand what conditions create the best devices.
%%<segue into simulation>

\subsection*{Molecular Dynamics}
%EJ: Here or above: Why MD the right tool?
Molecular dynamics (MD) is a simulation tool which uses classical physics and statistical thermodynamics to sample the equilibrium states of a thermodynamic ensemble.
The MD algorithm integrates Newton's equations of motion to update the particle positions.
This process can be iterated until the system reaches equilibrium.
MD is the right tool for looking at the bulk structure of an OPV because we can simultaneously probe the thermodynamics which govern OPV self assembly and the kinetics that follow the device processing.
Other tools, like Monte Carlo (MC), may allow us to sample equilibrium states of an ensemble, but we would lose information about the dynamics.
MC is also inefficient for polymers because perturbing a long chain of particles requires a ``cluster move'', which is not parallelizable.

@@

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}\label{bad}
    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from~\cite{punma}.}
\end{wrapfigure}

Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
\[
    U_{LJ}(r_{i,j}) = 4\epsilon\big[
        {\big(\frac{\sigma}{r_{i,j}}\big)}^{12}-
        {\big(\frac{\sigma}{r_{i,j}}\big)}^{6}
        \big]
\]
Where $i$ and $j$ are the particles separated by distance $r_{i,j}$.
The equilibrium distance between particles is controlled by $\sigma$ and the depth of the potential well is controlled by $\epsilon$ (see \autoref{lj}).
A distance cutoff, $r_{cut}$, is often used to reduce the number of pairwise interactions and improve performance.

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/lj.pdf}\label{lj}
    \caption{The Lennard-Jones potential with relevant distances labelled}
\end{wrapfigure}

Particles connected by bonds are also modelled by classical forces, for example the bond potential may be treated as a harmonic oscillator:
\[
    V_{bond}{(r)} = \frac{1}{2}k{(r-r_{0})}^{2}
\]
Where $r$ is the bond length, $r_{0}$ is the equilibrium bond length, and $k$ is the spring constant for the bond.
The angle potential is also treated as a harmonic oscillator:
\[
    V_{angle}{(\theta)}=\frac{1}{2}k{(\theta-\theta_{0})}^{2}
\]
Where $\theta$ is the angle formed between three bonded particles, $\theta_{0}$ is the equilibrium angle, and $k$ is the spring contant for the angle.
The dihedral potential can be defined by the follow Fourier series:
\[
    V_{dihedral}(\phi)=\frac{1}{2}k_{1}(1-\cos(\phi))+\frac{1}{2}k_{2}(1-\cos(2\phi))+\frac{1}{2}k_{3}(1-\cos(3\phi))\frac{1}{2}k_{4}(1-\cos(4\phi))
\]
Where $\phi$ is the angle between planes formed by particles in the dihedral (see \autoref{bad}) and $k_{n}$ are the force coeffients.

%% transition???
The first MD simulation modelled a system of 108 particles and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
Now GPUs are a 100 millions times faster.
%%<what is MD used for? why is MD the best technique for gettign these OPV morphologies?>
Due to its efficient scaling, MD is now commonly used for the modelling of protein folding~\cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.
By abstracting away some of the atomic degrees of freedom, MD can be used to look at even larger systems. %%transition attempt

@@

Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse grain site.
Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
%%<how do cg models let us access long length/time??>
Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest, we don't need to consider atomic level properties when we are interested in the bulk morphology\cite{Muller-Plathe2002}.
The heart of coarse graining is the removal of degrees of freedom. 
This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
Due to their long length and time scales, coarse grain models are ideal for examining polymer properties\cite{Gartner2019a}.
It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
Even if the simulation was to complete, there would be too much information to process accurately. 
Coarse graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.

The resolution of coarse grain systems is broad:
Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one site per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
%%<examples of cg models and the cool things they do>
General coarse grain models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
A coarse grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
%% transition?
Which model is right depends on the length and time scale on which the property of interest can be observed.

%%<multiscale sims>
For many systems, however, we are interested in properties which span length scales.
For instance, in a system like a OPV polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5--10 nm)\cite{Huang2010}; it is the wrong tool for the job.
If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily: a process called backmapping.
In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse grain structure.
The large length scale, polymer level properties can be equilibrated during the coarse grain simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores \textit{and} the connectivity of these chromophores over distances proportional to the exciton dissociation length.
%%<what stands in our way?>

@@

%%<segue from automated creation of forcefields to...>
%%<mapping operator has to be decided by hand> <is this section too big?>
Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse grain site and where the site is placed relative to the atom group.
Mapping operators are chosen based on the desired resolution of the coarse grain system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule for the MARTINI method, a user must pick a mapping and then compare the chemical structure of the resulting sites to those which have already been parameterized; a process which is time consuming and error prone\cite{martini-tutorial}.
The published tutorial recommends searching through existing MARTINI topologies to find similar structures and then manually editing them to fit the new molecule.
Whether the structure is similar then is based on the user's chemical knowledge, judgement, and intuition.
%%The MARTINI force field was first designed for lipids, further parameterization for proteins and nuclei acids has since been added, and it has been shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
Many other mapping schemes also rely on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend? What groups have the most dominant interactions in this structure). %%<cite any model where rings are one site><cite dna cg model>).
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a ``super atom''.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the ``best'' mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
Another uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the ``expert'' mapping chosen using chemical intuition reliably\cite{Li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
%%<how cg potentials have been attained> 
Deciding on a mapping operator is one part of creating a coarse grain model, the second step is to create an effective potential for the site.

@@

%% TODO
%% feedback from chris: Also, in the MSIBI section you could take a paragraph or 2 to define what an RDF is, what a Boltzman inverse is, what a potential mean force is, then go into the algorithm steps. I feel like defining those terms in a more general sense would be a good preface to describing the actual approach/steps used in the process. Also, one other question that popped up is how bonds and angles between coarse beads are handled in the MSIBI step.
There are numerous methods for deriving coarse grain potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
%%<IBI>
IBI is where a coarse grain potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
The RDF can be used to investigate properties such as the density or the phase of a system and the RDF is used in IBI as the target distribution for the non-bonded potentials. %%reword
The process for determining the non-bonded potentials using IBI is as follows:
\begin{enumerate}
    \item {The coarse grain system is mapped onto an equilibrated atomistic one.}
    \item {The average RDF of the mapped system is calculated over the equilibrated frames of the trajectory --- this is the target distribution.}
    \item{Taking the Boltzmann Inverse (see \autoref{pmf}) of the RDF results in the potential of mean force (PMF).
        \begin{equation}
            \label{pmf}
            F(r) = -k_{B}T \ln g(r)
            \tag{\ref{pmf}}
        \end{equation}
        Where $F(r)$ is the PMF, $k_{B}T$ is the thermal energy, and $g(r)$ is the target distribution.
        Although $F(r)$ is a free-energy and not a potential energy, it is sufficient to be used as the initial potential ($V_{0}$) in the iterative scheme\cite{Reith2003}.
        }
    \item{A simulation can be run using \autoref{pmf} as the non-bonded potential to achieve a new distribution.}
    \item{The difference between the new and target distribution can be accounted for in the next iteration accoring to \autoref{ibi}.
        \begin{equation}
            \label{ibi}
            V_{i+1}(r) = V_{i}(r) - k_{B}T \ln\big(\frac{g_{i}(r)}{g(r)}\big)
            \tag{\ref{ibi}}
        \end{equation}
        Where $g_{i}(r)$ is the distribution obtained using the potential $V_{i}(r)$.
        }
\end{enumerate}
This process is repeated until the difference between the result and the target is sufficiently small.

The coarse grain potential derived from IBI is not transferrable to different thermodynamic statepoints.
This is because the RDF is a property of the ensemble average at a given statepoint, so the potential derived from this property is also limited.
For example, separate potentials are required to capture solid and fluid structures of a pure simple lipid~\cite{Hadley2010a}.
There are many attempts to create transferrable CG potentials, for example:
The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}.
But optimization to the liquid-vapor equilibrium, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.
%%<so we probably want to create our own potentials>
%%<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.>~\cite{Moore2014}

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/moorefig.pdf}\label{moore}
    \caption{Visualization of the state space coverage of different potentials: if the thermodynamic states are too similar (b), then the overlap region is large enough that there are many potentials which will fit the target. Choosing states which are different (a) will better define the potential. Image adapted from ref~\cite{Moore2014}.}
\end{wrapfigure}

Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential\cite{Moore2014}.
The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid.
When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
If this overlap region is large, there are many potentials which will provide matching RDFs (see \autoref{moore}).
For some systems there may not be a potential that represents all states; this is not unique to coarse potentials, atomistic potentials also have this limitation.
%%<need some tie in back to why we would want to go from CG--->atomistic>

@@

As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the site chemistries. %%cite grits
This package will need further testing as it is tested on different compounds, but the proof of concept exists.

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}\label{hexane}
    \caption{Hexane chemical structure (top) overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}
\end{wrapfigure}
